---
title: "Group Project 2"
author: "Knut Gjertsen"
date: "12/3/2017"
output: html_document
---


## Libraries and Data Setup 
```{r}
library(lubridate)
library(gmodels)
library(ggplot2)
library(dplyr)
library(class)
library(gmodels)

listings <- read.csv("Listings2013.csv")
```

## Data Cleaning
```{r}

sapply(data, function(x) sum(is.na(x)))



listings$number_of_days <- NULL
listings$principal_balance <- NULL
listings$loan_status_description <- NULL
listings$prosper_rating <- NULL
listings$listing_monthly_payment <- NULL

listings$loan_status[listings$loan_status == 1] <- 0
listings$loan_status[listings$loan_status == 4] <- 0

listings$loan_status[listings$loan_status == 2] <- 1
listings$loan_status[listings$loan_status == 3] <- 1

listings$loan_origination_date <- as.Date(listings$loan_origination_date, "%d/%m/%Y")
listings$loan_origination_date <- as.numeric(listings$loan_origination_date)

# remove NAs
listings <- listings[complete.cases(listings),]


```
Scorex is the credit score of the user, it goes from < 600, to 778+. 
```{r}

scorex <- listings %>%
    group_by(scorex) %>%
    summarise(count = n())

plot<-ggplot(data=scorex, aes(x=scorex, y=count, fill =scorex))+
  geom_bar(stat="identity" , position = "dodge")
plot
```
 
Prosper Score is a score from 1-11 with 1 being lowest risk. Because this is a score that we did not create we don't know what went into it. In addition the data they are using is probably the same data we are using so it does not provide any novel new information to the model. Lets remove it.
```{r}
listings$prosper_score <- NULL
```

listings category ID is a category of the Loan but there is no description to go along with the IDs. This information might be useful though. NNot sure what to do with this.
```{r}

```

Income range, Income Range Description, Stated Monthly Income. We don't want this datapoint to be overrepresented in the model. Therefore we only need one of these variables. Lets go with Stated Monthly Income since it is more granular than the broad income range. 
TO DO: Some of the algorithms will find that they are highly correlated and won't "Count them as double"... which ones?
```{r}
listings$income_range   <- NULL
listings$income_range_description  <- NULL

income <- listings %>%
    group_by(stated_monthly_income) %>%
    summarise(count = n())

str(listings$stated_monthly_income)
plot<-ggplot(data=listings, aes(listings$stated_monthly_income))+
  geom_histogram(binwidth = 250) + xlim(0, 50000)
plot
```

Income Verifiable, looks good and useful. Have to modify to be a factor first. 
```{r}

listings$income_verifiable <- factor(listings$income_verifiable)

verifiable <- listings %>%
    group_by(income_verifiable) %>%
    summarise(count = n())

plot<-ggplot(data=verifiable, aes(x=income_verifiable, y=count, fill=income_verifiable))+
  geom_bar(stat="identity" , position = "dodge")
plot

plot<-ggplot(data= listings, aes(x=income_verifiable, y=stated_monthly_income)) + geom_boxplot()  +   coord_cartesian(ylim=c(0, 15000))
plot
```

DTI WProsper Loan, debt to income ratio.
```{r}
loanRatioOne <- listings %>%
    filter(dti_wprosper_loan > 1) %>%
    summarise(count = n())
loanMax <- listings %>%
    filter(dti_wprosper_loan == 1000000) %>%
    summarise(count = n())
loanInBetween <- listings %>%
    filter(dti_wprosper_loan < 1000000  & dti_wprosper_loan > 1) %>%
    summarise(count = n())



```
TO DO: Why does this have to be a value less than 1?


Employment Status Description & Employment.
There are blank values for occupation when someone chooses "Other for Employment Status Description". Lets fix this. 
```{r}


levels(listings$occupation)[levels(listings$occupation) == ""]<- "Other"

str(listings$employment_status_description)
levels(listings$employment_status_description)
levels(listings$employment_status_description)[levels(listings$employment_status_description) == "Not employed"] <- "Not-employed"


employment <- listings %>%
    group_by(employment_status_description) %>%
    summarise(count = n())

plot<-ggplot(data=employment, aes(x=employment_status_description, y=count, fill=employment_status_description))+
  geom_bar(stat="identity" , position = "dodge")
plot

```


## Data Models

# Data Prediction using Logistic Regression

```{r}
# logit.model <- glm(loan_status ~ ., data = listings, family = "binomial")
# summary(logit.model)

# Predicting the probability of an employee leaving using the Logit model
# listings_logit <- NULL
# listings_logit$loan_status <- predict(logit.model, newdata = listings, type = "response")

# Converting probabilities to a binary outcome (1 for Prob > 0.5, otherwise 0)
# listings_logit$loan_status[listings_logit$loan_status > 0.5] <- 1
# listings_logit$loan_status[listings_logit$loan_status != 1] <- 0

# Creating a cross table to verify the accuracy of the Logit model
# CrossTable(x = listings_logit$loan_status, y = listings[26834:33542, 11], prop.chisq = FALSE)
```

# Getting Data Ready for Machine Learning Models

```{r}
# Randomizing  dataset
listings_random <- listings[sample(nrow(listings)),]

# Rescaling listings dataset using Min-Max Normalization
normalize <- function(x) {
  return ((x - min(x)) / (max(x) - min(x)))
  }
listings_n <- as.data.frame(lapply(listings_random[31:40], normalize))
str(listings_n)

# Subsetting listings dataset with 33542 enteries into test and train subsets, where 80% entries (26,833) are test and 20% entries (6,709) are train
listings_train <- listings_n[1:26833, 1:10]
listings_train_label <- listings_random[1:26833, 3]

listings_test <- listings_n[26834:33542, 1:10]
listings_test_label <- listings_random[26834:33542, 3]

```

# Data Prediction using kNN

```{r}
listings_predict <- knn(train = listings_train, test = listings_test,
                      cl = listings_train_label, k = 183) 
                      # k = sqrt(population size: 33542) = 183 
# confusion matrix
CrossTable(x = listings_test_label, y = listings_predict, 
           prop.chisq=FALSE)
```



